### 2016-06-30 Projects/Exploratory_Convective_PPE/Report/convective_ppe_heating.tex
minor edit to ppe report
Update BIB and PPE
added Klaene ref   and acknowledge

@@

>>>>

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../../../Projects/Gear_Plunge_Tests/Figures/Plunge_2}
\caption{Image of plunge test apparatus configured to test a turnout gear sample.}
\label{fig:plunge_pic}
\end{figure}

@@

The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Keith Stakes (currently with UL FSRI), Nicholas Dow (SURF student), and Jay MCElroy (retired) from NIST for their contributions in preparing and conducting these experiments. These experiments could not have been conducted without them.

Appreciation is extended to Firefighter Jacob Hoffman, Toledo Fire Department, Deputy Chief Cecil Clay (ret), Oklahoma City Fire Department, Director John Culbertson, Montana State University Fire Services Training School and their organizations for their support of this research.

The Delaware County Emergency Services Training Center provided the location and logistical support for these experiments.  The Delaware county team was under the direction of Kerby Kerber.  For construction and test support the team included: Joe Bingham, Dave Wright, Dave Nercesian (small engine repair), Mike Gura, Scott Wiercinski, Bill Fields (Fields Fire Protection).  We also thank the dedicated team of fire instructors and firefighters that supported these experiments; Brian Righter (Rudy), John McGowan, Matthew Poissant, John Frey, Brian Embert, Raymond Keller III, Mike Bramble, Edward McBride, Mark Morrissey, Bill Norris, and Matt LeTourneau.

Thank you for assisting NIST in generating data that will assist the fire service in making tactical choices.
